\section{12th March 2023: Triad of Evil}
\subsection*{Text: Revelation 12:1-13:18}
  \begin{quote}
    [1] And a great sign appeared in heaven: a woman clothed with the sun,
    with the moon under her feet, and on her head a crown of twelve stars.
    [2] She was pregnant and was crying out in birth pains and the agony of
    giving birth.  [3] And another sign appeared in heaven: behold, a great
    red dragon, with seven heads and ten horns, and on his heads seven
    diadems.  [4] His tail swept down a third of the stars of heaven and cast
    them to the earth.  And the dragon stood before the woman who was about
    to give birth, so that when she bore her child he might devour it.  [5]
    She gave birth to a male child, one who is to rule all the nations with a
    rod of iron, but her child was caught up to God and to his throne, [6]
    and the woman fled into the wilderness, where she has a place prepared by
    God, in which she is to be nourished for 1,260 days.

    [7] Now war arose in heaven, Michael and his angels fighting against the
    dragon.  And the dragon and his angels fought back, [8] but he was
    defeated, and there was no longer any place for them in heaven.  [9] And
    the great dragon was thrown down, that ancient serpent, who is called the
    devil and Satan, the deceiver of the whole world—he was thrown down to
    the earth, and his angels were thrown down with him.  [10] And I heard a
    loud voice in heaven, saying, “Now the salvation and the power and the
    kingdom of our God and the authority of his Christ have come, for the
    accuser of our brothers has been thrown down, who accuses them day and
    night before our God.  [11] And they have conquered him by the blood of
    the Lamb and by the word of their testimony, for they loved not their
    lives even unto death.  [12] Therefore, rejoice, O heavens and you who
    dwell in them!  But woe to you, O earth and sea, for the devil has come
    down to you in great wrath, because he knows that his time is short!”

    [13] And when the dragon saw that he had been thrown down to the earth,
    he pursued the woman who had given birth to the male child.  [14] But the
    woman was given the two wings of the great eagle so that she might fly
    from the serpent into the wilderness, to the place where she is to be
    nourished for a time, and times, and half a time.  [15] The serpent
    poured water like a river out of his mouth after the woman, to sweep her
    away with a flood.  [16] But the earth came to the help of the woman, and
    the earth opened its mouth and swallowed the river that the dragon had
    poured from his mouth.  [17] Then the dragon became furious with the
    woman and went off to make war on the rest of her offspring, on those who
    keep the commandments of God and hold to the testimony of Jesus.  And he
    stood on the sand of the sea.

    [1] And I saw a beast rising out of the sea, with ten horns and seven
    heads, with ten diadems on its horns and blasphemous names on its heads.
    [2] And the beast that I saw was like a leopard; its feet were like a
    bear’s, and its mouth was like a lion’s mouth.  And to it the dragon gave
    his power and his throne and great authority.  [3] One of its heads
    seemed to have a mortal wound, but its mortal wound was healed, and the
    whole earth marveled as they followed the beast.  [4] And they worshiped
    the dragon, for he had given his authority to the beast, and they
    worshiped the beast, saying, “Who is like the beast, and who can fight
    against it?”

    [5] And the beast was given a mouth uttering haughty and blasphemous
    words, and it was allowed to exercise authority for forty-two months.
    [6] It opened its mouth to utter blasphemies against God, blaspheming his
    name and his dwelling, that is, those who dwell in heaven.  [7] Also it
    was allowed to make war on the saints and to conquer them.  And authority
    was given it over every tribe and people and language and nation, [8] and
    all who dwell on earth will worship it, everyone whose name has not been
    written before the foundation of the world in the book of life of the
    Lamb who was slain.  [9] If anyone has an ear, let him hear:

    [10] If anyone is to be taken captive,
        to captivity he goes;
    if anyone is to be slain with the sword,
        with the sword must he be slain.

    Here is a call for the endurance and faith of the saints.

    [11] Then I saw another beast rising out of the earth.  It had two horns
    like a lamb and it spoke like a dragon.  [12] It exercises all the
    authority of the first beast in its presence, and makes the earth and its
    inhabitants worship the first beast, whose mortal wound was healed.  [13]
    It performs great signs, even making fire come down from heaven to earth
    in front of people, [14] and by the signs that it is allowed to work in
    the presence of the beast it deceives those who dwell on earth, telling
    them to make an image for the beast that was wounded by the sword and yet
    lived.  [15] And it was allowed to give breath to the image of the beast,
    so that the image of the beast might even speak and might cause those who
    would not worship the image of the beast to be slain.  [16] Also it
    causes all, both small and great, both rich and poor, both free and
    slave, to be marked on the right hand or the forehead, [17] so that no
    one can buy or sell unless he has the mark, that is, the name of the
    beast or the number of its name.  [18] This calls for wisdom: let the one
    who has understanding calculate the number of the beast, for it is the
    number of a man, and his number is 666.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{All the numbers and imagery here are symbols and should not be taken
  literally.  However, the struggle between good and evil here are spiritual
  realities.}
  \item{First, the woman represents the community of the true Israel (those
  from the visible covenant community of God with true faith).  Here, the
  twelve stars are like a throwback to Joseph's dream, and hence represent
  the twelve tribes of Israel.  We know this because the woman's Son is
  Jesus.  The woman doesn't need to be specifically identified with Mary,
  because while it is true that Mary was the one who gave birth to Jesus, it
  is also true that Jesus came out of Israel.  The birth pains here then
  refer to the sufferings of the community of the true Israel.  By the way,
  since the Church is the true Israel (c.f Romans 11), the woman can also be
  identified with the Church.  And yes, the second charater here is the
  woman's Son, who is Jesus.  The third character here is about the dragon,
  who is the primordial evil.  The dragon here has two subordinates, and as
  we will see in chapter 13, one is from the sea and one is from the land.}
  \item{Three points for today:
  \begin{itemize}
    \item{Rage of the dragon.  The dragon wants to take out his rage against
    the woman and her Child because he lost a decisive battle.}
    \item{Resemblance of the beast to the dragon and to what is real and good.}
    \item{Refuge.  God has provided a place of refuge for the woman (who is a
    representation of the elect from God's visible covenant community).}
  \end{itemize}}
  \item{The rage of the dragon; one interpretation is that the dragon tried
  to get rid of Jesus via King Herod and etc etc, but he failed.  In fact, he
  was defeated by the ``blood of the lamb'' (v11).  I.e, Jesus death on the
  cross and his subsequent resurrection and exaltation defeated the beast.
  So after his failure to kill the woman's Son, he tried instead to persecute
  the woman.  I.e, the dragon now persecutes the true people of God.  The
  dragon here is said to have swept down a third of the stars of heaven,
  which could be bad angels or just people who have pledged their allegiance
  to the dragon.  The imagery of the flood here represents evil and chaos,
  which the dragon uses to persecute the people of God.  }
  \item{The dragon does not act alone though; the dragon has two lieutanents,
  the beast from the sea and the beast from the land.  The first beast from
  the sea is a throwback to Daniel $7$, and the first beast has a big
  resemblance to the dragon, since the dragon gave his authority to the
  beast.  The first beast also persecuted the people of God just like what
  the dragon did.}
  \item{The beast from the sea also copies what God does in Revelation 7 to
  mark his followers with a mark.  Only those who have been marked by the
  first beast can buy and sell things.  That is a cheap imitation of what God
  did.  But in the end, it will only be shown to be a cheap imitation.  This
  sea beast is also able to perform signs like healing and things like that,
  which is how he is able to scam the people of the world to believe him.  }
  \item{The sea beast is to be represented with a man.  I.e, in verse 18 of
  chapter 13, the number $6$ is to be identified with a man, and the sea
  beast has the number $666$.  Hence, the sea beast is to be identified with
  a very outstanding man.  The sea beast here is then the Antichrist (with a
  big A).  In the past, popular interpretations of this man were the Roman
  emperors, and etc.  We don't need to fret too hard about the specific
  identity of this Antichrist, but we just need to be aware that even now,
  the spirit of the Antichrist is at work through the mini antichrists (small
  A) that are already now at work as John says in $1$ John.  }
  \item{The dragon also has a beast from the land.  The land beast is like
  the subordinate to the sea beast, and can hence be identified with a false
  prophet.  The land beast here promotes worship of the sea beast, and the
  land beast here exercises the authority of the sea beast.  The land beast
  also creates images of the sea beast and causes people to worship the sea
  beast. The land beast is the purveyor of all false teaching. Even now, we have such people in our churches who preach false gospels.}
  \item{Now, as the people of God, how can we stand in the presence of this
  triad of evil (Dragon, sea beast, land beast).  Just as the woman fled into
  the wilderness (throwback to Israel's exodus journey) where she has a place
  prepared by God, we must do the same when there is danger. Whenever we feel tempted or persecuted, we must flee to God where God will protect us. We note that the woman is to be nourished for $1260$ days, and we note also that the beast was allowed to exercise authority for $42$ months (1260 days). That is, for as long as the beast is persecuting us, God will be our refuge. }
  \item{In short, though we know that evil will come, we can have confidence
  that God will protect us when we flee to Him.  And we must also be
  discerning to discern good from evil, because the evil that the beast
  brings will look a lot like good. We should not be too awed by false teachers who might be exceptional men, full of charisma, but we should listen to faithful teachers who might not be as exceptional.}

\end{itemize}