\setcounter{figure}{0}

\section{31st December 2023: Unwrapping God's gift}
\subsection*{Text: Galatians 4:4-7}
  \begin{quote}
    [4] But when the fullness of time had come, God sent forth his Son, born of woman, born under the law, [5] to redeem those who were under the law, so that we might receive adoption as sons. [6] And because you are sons, God has sent the Spirit of his Son into our hearts, crying, “Abba! Father!” [7] So you are no longer a slave, but a son, and if a son, then an heir through God.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{The wisdom of the world is that one needs to be good to receive good gifts. E.g, in the song “santa claus is coming to town”. I.e, legalism.}
  \item{Similarly, in Galatians, we have a similar problem; we have the judaizers preaching a false gospel to the Galatian Christians, telling them that one has to obey the requirements of the Mosaic Law to be saved. This would contradict the ides of the sufficiency of Christ. This is why Paul said what he said in our text, to refute the Judaizers.}
  \item{In our text, we see that Jesus was born of a woman (Mary). Jesus was born under the Mosaic Law.}
  \item{The Law was given to God’s people to guide them to do that is right, but the Law could not give people the ability and the strength to do what is right. But God’s people perverted the Law, and used their obedience to the Law as a bargaining chip to earn God’s favour and promises (which were to be given to them through grace! And they also didnt fully obey the Law anyway).}
  \item{The Law was given to teach people about sin and to lead to humility and contrition (extrapolation from ch3:19). But being misused, the Law had become a source of pride, when people think they are better cause of their supposed better obedience.}
  \item{In this sense, the Law had become a source of bondage, when it leads to prideful thinking and when it leads to one trying to earn their justification through the Law.}
  \item{Jesus was born under the Law so He could identify with all of us under the Law, so as to be able to redeem us from the Law. He did this by the mechanism described in ch3:13-14, i.e by “becoming a curse for us”. See also the rest of the book. }
  \item{So now all of us are free from needed to earn our justification through the Law, because of what Jesus did for us.}
  \item{So here we see the problem of the Judaizers. The Judaizers were trying to bring the Galatian Christians back under bondage to the Law, when Jesus had already freed them from the Law.}
  \item{When Jesus has redeemed us, God also sends His Holy Spirit into our lives to transform us and to make us His children. One mark of that is that we view God as our Father, that we instinctively cry out to God as our Father. And as children of God, the Spirit slowly transforms us to live more and more like Jesus. }
  \item{The Holy Spirit lives within all of us. The Holy Spirit guides us to follow God’s will, the Spirit helps us to pray, and the Spirit prompts us and nudges us onto the paths of righteousness. But from time to time we ignore the Holy Spirit’s voice. We should not do that! If we listen to the voice of the Holy Spirit within us, we will be transformed.}
\end{itemize}