\setcounter{figure}{0}

\section{18th February 2024: Blessed beyond measure}
\subsection*{Text: Numbers 6:22-27}
  \begin{quote}
    [22] The LORD spoke to Moses, saying, [23] “Speak to Aaron and his sons, saying, Thus you shall bless the people of Israel: you shall say to them,

    [24] The LORD bless you and keep you;
    [25] the LORD make his face to shine upon you and be gracious to you;
    [26] the LORD lift up his countenance upon you and give you peace.

    [27] “So shall they put my name upon the people of Israel, and I will bless them.”
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{In CNY, we toss yusheng. Each ingredient is associated to a particular blessing. This invites us to think about our view of blessing as christians.}
  \item{Three questions to ask as we think about blessing today:
    \begin{enumerate}
      \item Where is blessing to be found?
      \item What do we understand by blessing
      \item How can we receive this blessing
    \end{enumerate}}
  \item{The ancient priestly blessing was given by moses by God to aaron, for aaron was to bless them with that blessing. This was relevant because israel was in the toughest times in the past, being in the exile. In our troubled world, we also want to ask: where is blessing to be found?}
  \item{From our text, we know that true blessing comes only from YAHWEH, and the tetragrammaton is spelled as LORD in the english. For example, all the blessings in our text starts with the LORD. }
  \item{Here, we see that the blessing is secondary, the focus here is on the LORD. Why is there so much emphasis on where our blessing comes from? This is because instead of seeking blessing from God, we often seek blessing from elsewhere. E.g, we often seek our significance and our blessing from material possessions. Sometimes we feel that if we just have a nice house, then we will be blessed. E.g, we also often seek blessing from relationships, e.g we find our true blessedness in our wife/husband, in desiring a kid, etc. If we think of blessing only in these measures, we can’t say that we are blessed beyond measure. This is brcause our desire is an endless pit, we can always desire more things, more wealth more health etc. But if we think of blessing as coming from the LORD, if we think of the LORD as our blessing, then we can say we will be blessed beyond measure.}
  \item{The LORD knows all our needs, He knows that we need His protection and provision. If we can see provision and protection as coming from God, then we are blessed. We see this in the Lord’s prayer, “give us this day our daily bread” and “keep us from temptation”. }
  \item{The idea of blessing as coming from the LORD is described in two vivid metaphors in our text. First, we have “the LORD make his face shine upon you”. When do people’s face shine? E.g, a kid opening a new present in delight, a couple looking at each other in delight, etc. The heart of blessing is this: God delights in us so much that metaphorically, His face shines on us. This means that we have God’s favour, even though we don’t deserve it. This is the heart of blessing.}
  \item{The next metaphor is: “the Lord lift up his countenance upon you”. This means that God’s eyes are always on us, which gives us peace (shalom). This is in contrast to pagan religions, where their deity has to be provoked to action through many religious rites. Here, God graciously shines his covenant to us first.}
  \item{So, what is blessing from a Christian POV?
  \begin{itemize}
    \item{To know the LORD's protection and provision but more importantly to know his presence (to have that face to face relationship with him) where we can experience his peace.}
  \end{itemize}}
  \item{How do we receive this blessing of God?
  \begin{itemize}
    \item{ In the OT, it is through obedience to the Law. And disobedience to
    the Law would lead to cursing. And we see that was what happened to the
    Israelites, God’s face turned away from them. And this is what would have
    happened to us too due to our sin, if not for God’s grace.}
    \item{In God’s grace, God instituted a new covenant, where there is forgiveness of sin when we believe in His Son, whom God has sent to be the propitiation for our sin. In the past, God’s face would be turned away from us because of our sin, but now, with Jesus, God’s face is turned towards us cause we are in Jesus.}
  \end{itemize}}
  \item{When God blesses us, there is a missional purposes. Wrt Psalm 67 (our scripture reading text), when God blesses us, we are to be a blessing to others. We are blessed to be a channel of God’s blessing to others. When God shines his face on us, we can show practical love to our neighbours so that they can see God’s love through our actions, like the good samaritan. And when God shines his face on us, we can show God’s love to our neighbours by sharing the gospel to them.}
  \item{Also, in the life to come, when Jesus returns, we will experience the full extent of Aaron’s blessing. When Jesus comes again, we will be before God’s face, we will see God face to face, there will be no more evil and sin and thus no more tears. Thus, we can look forward to this final blessed state when Jesus comes again.}
  \item{Thus, for those who do not believe in Jesus, you need to believe in Jesus to receive true blessing. For those who believe in Jesus, we need to self-examine to see if we are seeking for blessing apart from God. When we seek blessing in God, we realise that God is the source of provision and protection, and more importantly, we can experience God’s presence. This is even when we experience difficult things like Job. When we get bad things we don’t want or when we dont get good things we want, it is because God knows that is good for us, and that through our experience of pain and suffering, He is mysteriously working our our shalom in the background. And that He is with us, His presence and peace is with us. And that is blessing.}
\end{itemize}