\section{6th November 2022: Is God calling you?}
\subsection*{Text: Acts 13:1-4}
  \begin{quote}
    [1] Now there were in the church at Antioch prophets and teachers, Barnabas, Simeon who was called Niger, Lucius of Cyrene, Manaen a lifelong friend of Herod the tetrarch, and Saul. [2] While they were worshiping the Lord and fasting, the Holy Spirit said, “Set apart for me Barnabas and Saul for the work to which I have called them.” [3] Then after fasting and praying they laid their hands on them and sent them off.

    [4] So, being sent out by the Holy Spirit, they went down to Seleucia, and from there they sailed to Cyprus.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{Point 1: Diverse group of church members.
  \begin{itemize}
    \item{Today’s topic is about mission Acts 1-12 is about Peter’s mission
    to the Jews at Jerusalem.  Acts 13-28 is about Paul’s mission to the
    Gentiles, beginning at Antioch.}
    \item{Firstly, we see that the church at Antioch was a missionary church.
    Antioch was the cradle of world missions.  This church had a very diverse
    group of members.  The five people mentioned had gifts of prophecy and
    teaching.  Barnabas is the first name listed here.  He was identified as
    early as Acts 4.  He was described as a Jewish man of Levitical heritage.
    Barnabas’ name means “son of encouragement” Simeon and Lucius were quite
    cross-cultural.  They weren’t Jews.  Especially Simeon, who is from
    Africa.  Then there was Manean, who knew Herod, but didnt turn out like
    him.  Wew.  Then finally, there was Saul.}
    \item{These are the people who were members of the church at antioch.
    But they also felt that God was calling the church at Antioch to
    something greater, and they wanted to be part of it.  In comparison, we
    are quite slothful in our zeal for God… A church who is not participating
    in the great commission is participating in the great omission instead…}
  \end{itemize} }
  \item{Point 2: What in the world am I doing for God's mission?
  \begin{itemize}
    \item{If God is calling you, it is through the church. Like how the prophecy came to the church at antioch. If you want to know if you are called, check with the church… the church community and the elders will let you know.}
    \item{Just like how Paul and Barnabas were set apart by God, even before they were born, so are we. We were set apart to do God’s work.}
    \item{For us, ordinarily, we need to be martyrs at home first before we can be martyrs outside in the field. The local church gives us a good opportunity to learn self denial. Once we learnt that, we can go out in the field.}
    \item{How do i know Gods will for my life?  The Holy Spirit who helps us
    to interpret God’s word as well as the circumstances in our lives.  We
    need to follow the leading of the Spirit to see where God wants to lead
    us to do His work.}
    \item{Sometimes God might lead us to the marketplace, and that is ok. But God calls some people out into the field and for full time ministry. We must be sensitive to this leading.}
  \end{itemize} }
  \item{Point 3: The commission.
  \begin{itemize}
    \item{From v3-4, we see the church commissioning Paul and Barnabas and
    etc for mission.  These dudes had the authority of Christ’s church.  The
    church is not obliged to send all who think they are called.  If church
    sends some people who aren’t equipped, they might burden the mission.  So
    the church plays an important role in discerning.}
    \item{If a church is not mission minded, it is not a church!}
    \item{A word to parents: parents have a role to play to encourage children to be interested in missions. One small way is to host missionaries. Or to pray for the missionaries by name. These kids are our future pastors and missionaries.}
    \item{A word to young people: take a gap year or what to do missions? Is ok one!}
    \item{A word to retirees: y’all have a lot of experience. Don’t spend all of the experience at the golf course or the kopitiam. Maybe God wants to send you overseas to share the love of Christ. God can use you powerfully even in your old age.}
    \item{To discern your calling, lots of prayer and fasting is required!}
    \item{From the Isaiah story in Isaiah 6, we see that if we love God enough to worship him, then we will love God enough to be sent by him.}
  \end{itemize}
  }
\end{itemize}