\section{27th November 2022: Do not be afraid, Zechariah}
\subsection*{Text: Luke 1:5-25}
  \begin{quote}
    [5] In the days of Herod, king of Judea, there was a priest named
    Zechariah, of the division of Abijah.  And he had a wife from the
    daughters of Aaron, and her name was Elizabeth.  [6] And they were both
    righteous before God, walking blamelessly in all the commandments and
    statutes of the Lord.  [7] But they had no child, because Elizabeth was
    barren, and both were advanced in years.

    [8] Now while he was serving as priest before God when his division was
    on duty, [9] according to the custom of the priesthood, he was chosen by
    lot to enter the temple of the Lord and burn incense.  [10] And the whole
    multitude of the people were praying outside at the hour of incense.
    [11] And there appeared to him an angel of the Lord standing on the right
    side of the altar of incense.  [12] And Zechariah was troubled when he
    saw him, and fear fell upon him.  [13] But the angel said to him, “Do not
    be afraid, Zechariah, for your prayer has been heard, and your wife
    Elizabeth will bear you a son, and you shall call his name John.  [14]
    And you will have joy and gladness, and many will rejoice at his birth,
    [15] for he will be great before the Lord.  And he must not drink wine or
    strong drink, and he will be filled with the Holy Spirit, even from his
    mother’s womb.  [16] And he will turn many of the children of Israel to
    the Lord their God, [17] and he will go before him in the spirit and
    power of Elijah, to turn the hearts of the fathers to the children, and
    the disobedient to the wisdom of the just, to make ready for the Lord a
    people prepared.”

    [18] And Zechariah said to the angel, “How shall I know this?  For I am
    an old man, and my wife is advanced in years.” [19] And the angel
    answered him, “I am Gabriel.  I stand in the presence of God, and I was
    sent to speak to you and to bring you this good news.  [20] And behold,
    you will be silent and unable to speak until the day that these things
    take place, because you did not believe my words, which will be fulfilled
    in their time.” [21] And the people were waiting for Zechariah, and they
    were wondering at his delay in the temple.  [22] And when he came out, he
    was unable to speak to them, and they realized that he had seen a vision
    in the temple.  And he kept making signs to them and remained mute.  [23]
    And when his time of service was ended, he went to his home.

    [24] After these days his wife Elizabeth conceived, and for five months
    she kept herself hidden, saying, [25] “Thus the Lord has done for me in
    the days when he looked on me, to take away my reproach among people.”
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{What can we know about Zechariah, from these verses?  First of all,
  levitical law states that a priest has to marry someone from the tribe of
  Aaron, and that is exactly what happened, which is a blessing.  However,
  Elizabeth was barren, which was a disgrace in those days.  But Zechariah
  was faithful to Elizabeth despite that (unlike Abraham and Sarah).
  Elizabeth's barrenness was not because of any curse or what, because both
  Elizabeth and Zechariah were blameless. Elizabeth's barrenness was because God wanted to do something amazing with her in her old age. }
  \item{According to Levitical law instituted in the time of Moses (and
  restored in the time of Ezra), the sons of Aaron were split into $24$
  divisions to serve in the temple all year round.  One of the duties was to
  burn incense.  According to Jewish tradition, the duty to burn incense is
  alloted to people by drawing lots, and it is a privilege to burn incense at
  the temple (people can only do this once a year).  So Zechariah was
  surprised when he saw someone else in the temple.}
  \item{Now, one view is that Zechariah had been praying for a son.  Yet when
  Gabriel announced the good news that his prayer was answered, Zechariah did
  not really believe.  In this view, Zechariah was skeptical and hence,
  Zechariah was judged for his lack of faith and was rendered mute for a
  time.}
  \item{Another view is that Zechariah was praying for the consolation of his
  people Israel, in the time of Herod (Herod was essentially a puppet
  installed by the Romans, Herod wasn't even from the Davidic line!  So Herod
  cannot be truly called king of Israel).  Under this view, in Zechariah's
  response, it seemed that there were two thoughts.  First of all was,
  Elizabeth is old, which means that it is unlikely that Elizabeth would have
  a son.  Secondly, Zechariah says that he himself is old, which means that
  it is unlikely for him to see and know whether what Gabriel has said would
  come to pass.  In fact, John the baptist was probably orphaned at a young
  age, which was why he grew up in the wilderness.  But anyway, under this
  view, Zechariah is not being skeptical but he was actually asking a sincere
  question.  And on this view, Zechariah being mute was not judgment from God
  for his unbelief but him being mute was a means of God's grace.  Zechariah
  being mute is a means of God's grace in the sense that:
  \begin{enumerate}
    \item{Him being muted was a supernatural sign.  If one supernatural sign
    can happen to him, surely another can.  Hence, him being muted was God
    confirming to Zechariah what He said through Gabriel.}
    \item{Him being muted led to him being unable to answer the people
    outside.  To the people outside, it would have looked like God's
    judgment.  So probably the people would have avoided Zechariah and hence
    gave him space/time to make babies lol.}
  \end{enumerate}
  Anyway under this view Zechariah could have prayed for a son too in his
  early years. }
  \item{``I am Gabriel''.  The same Gabriel that interpreted Daniel's dream
  was sent also to Zechariah.}
  \item{Possible lesson for us: we should not be too quick to judge, especially when bad things happen to others. We should not assume that it is God's judgement when bad things happen to good people.}
  \item{Another lesson for us: Zechariah prayer for a son was finally fulfilled after so long. Though Zechariah's prayer went unanswered for a long time, he was faithful to his wife (unlike Abraham) and he was faithful in temple service. So similarly to us, when we pray for things, we should continue to be faithful in other areas of our life.}
\end{itemize}