\section{25th December 2022: Ironies surrounding Christmas}
\subsection*{Text: Luke 2:1-21}
  \begin{quote}
    [1] In those days a decree went out from Caesar Augustus that all the world should be registered. [2] This was the first registration when Quirinius was governor of Syria. [3] And all went to be registered, each to his own town. [4] And Joseph also went up from Galilee, from the town of Nazareth, to Judea, to the city of David, which is called Bethlehem, because he was of the house and lineage of David, [5] to be registered with Mary, his betrothed, who was with child. [6] And while they were there, the time came for her to give birth. [7] And she gave birth to her firstborn son and wrapped him in swaddling cloths and laid him in a manger, because there was no place for them in the inn.

    [8] And in the same region there were shepherds out in the field, keeping watch over their flock by night. [9] And an angel of the Lord appeared to them, and the glory of the Lord shone around them, and they were filled with great fear. [10] And the angel said to them, “Fear not, for behold, I bring you good news of great joy that will be for all the people. [11] For unto you is born this day in the city of David a Savior, who is Christ the Lord. [12] And this will be a sign for you: you will find a baby wrapped in swaddling cloths and lying in a manger.” [13] And suddenly there was with the angel a multitude of the heavenly host praising God and saying,

    [14] “Glory to God in the highest,
        and on earth peace among those with whom he is pleased!”


    [15] When the angels went away from them into heaven, the shepherds said to one another, “Let us go over to Bethlehem and see this thing that has happened, which the Lord has made known to us.” [16] And they went with haste and found Mary and Joseph, and the baby lying in a manger. [17] And when they saw it, they made known the saying that had been told them concerning this child. [18] And all who heard it wondered at what the shepherds told them. [19] But Mary treasured up all these things, pondering them in her heart. [20] And the shepherds returned, glorifying and praising God for all they had heard and seen, as it had been told them.

    [21] And at the end of eight days, when he was circumcised, he was called Jesus, the name given by the angel before he was conceived in the womb.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{Point 1: the great is not the greatest after all.
  \begin{itemize}
    \item{Caesar Augustus thought he was powerful, his decree made the entire
    world move.  But actually, caesar Augustus’ census, which was a display
    of his authority, ironically is a display of God’s sovereignty, because
    God used caesar’s census to make it such that Jesus was born in
    Bethlehem.}
    \item{God can use even the self-serving actions of non-believers to
    accomplish His purposes in this world.  E.g, war in Ukraine.  The war is
    due to the sinfulness and fallenness of Man.  Suffering is bad.  But God
    can use this suffering to fling open doors for the gospel.  Everything
    that the Enemy uses for evil, God uses for good in a way that we can’t
    see.}
  \end{itemize}}
  \item{Point 2: the greatest news is delivered to the lowliest people.
  \begin{itemize}
    \item{Normally, we would expect important news to be announced first to
    important people.  E.g, if a principal has an announcement to make, he
    would first tell the HODs, not the gardeners, cause the HODs are higher
    up in the hierachy.  Here too, we see the good news first proclaimed to
    the shepherds, who were the poor and despised in society, since they were
    regarded as unclean (they are just abit higher than lepers).}
    \item{This shows that the kingdom of God isn’t just for those who are considered as “insiders”, but for the “outsiders”. The last will be first, and the first will be last.}
    \item{Jesus is not only the good shepherd, but Jesus is the perfect Lamb
    of God.  Makes sense that shepherds will go see a Lamb, haha (this point is pretty cute, dunno what to make of it).}
    \item{Of course, the shepherds were probably not expecting the Lamb of
    God, they were expecting a messiah that would bring political and
    military deliverance and to establish a kingdom just for the Jews.  But
    yet, we know that Jesus is not only the Lord of the Jews, but of the
    Gentiles too.}
  \end{itemize}}
  \item{Point 3: Creator becoming the created.
  \begin{itemize}
    \item{Jesus had to take on human nature, to fully identify with us.
    Jesus, the Word of the Father, consubstantial with the Father, took unto
    himself to a finite and weak human body in the form of a baby.  This
    allowed Jesus to take on our sins and suffer on the cross, to conquer
    death on our behalf by dying and resurrecting.  }
    \item{This allows us to have peace with God, which Jesus was supposed to
    bring (Luke 2:14).  And this also leads to peace among men.  When we
    truly believe that our sins are forgiven and that God loves us, we can
    have peace in our hearts no matter what happens to us.}
  \end{itemize} }
  \item{Point 4: No room for the Maker of the universe.
  \begin{itemize}
    \item{There was no room in the inn, which was more like a guesthouse than
    a motel.  The guesthouse was probably too crowded because of the census
    and how everyone returned to Bethlehem.  It was already a large
    condescension for Jesus to take on human nature.  It is even more humble
    of Jesus that Jesus chose to be born as a manger, when as royalty (King
    of the world + fulfilment of the Davidic King promise), Jesus should have
    been born in a nicer place.}
    \item{Christ humbled himself in this way to show us what kind of messiah
    He would be in His first coming.  And hence, we should follow Jesus'
    example as Christians (Philippians 2:4-11), to be humble.}
  \end{itemize} }
  \item{Point 5: gospel call/reflection:
  \begin{itemize}
    \item{Do we make room for Jesus in our conduct?  In our thoughts?  Or
    have we made room for Jesus before, but that room has been crowded out by
    the cares of the world.}
    \item{The shepherds made room for Jesus in their hearts through their
    faith, and as a result, they witnessed to others about Jesus and they
    worshipped Jesus.  On the other hand, there were others who wondered by
    didn’t necessarily believe (v18).  Well, you can’t wonder forever; you
    must eventually decide to believe this good news, or to not believe and
    hence die in your sins.}
    \item{Mary treasured up all the shepherds have said, and pondered them in
    her heart.  In other words, she believed the shepherds in order that she
    might understand.  So similarly for us, our feeble mind can’t fully grasp
    the wisdom of the infinite God, but God has revealed enough for us to
    believe first, and as we believe, we will slowly understand.  Faith
    seeking understanding, as Anselm puts it: “i do not seek to understand in
    order to believe, but I believe in order that I might understand”.
    Hence, if we haven’t made room in our hearts for Jesus, we must.}
  \end{itemize}}
\end{itemize}