\section{6th February 2022: A disciple's heart}
\subsection*{Text: Proverbs 4:20-27}
\begin{quote}
    [20] My son, be attentive to my words;
        incline your ear to my sayings.
    [21] Let them not escape from your sight;
        keep them within your heart.
    [22] For they are life to those who find them,
        and healing to all their flesh.
    [23] Keep your heart with all vigilance,
        for from it flow the springs of life.
    [24] Put away from you crooked speech,
        and put devious talk far from you.
    [25] Let your eyes look directly forward,
        and your gaze be straight before you.
    [26] Ponder the path of your feet;
        then all your ways will be sure.
    [27] Do not swerve to the right or to the left;
        turn your foot away from evil.
\end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{The key point of today's text is verse 23.  For the ancient
  Israelites, faith is not separated from knowledge and not separated from
  one's experience of the world.  Two points today: guarding the heart, and
  acting in wisdom.  Btw, the word ``heart'' here refers not to the physical
  heart, but to the entire inner life of the person.}
  \item{Wisdom starts with inclining our ears to our parent's saying.  That's
  how we learnt things like ``don't touch the hot stove'' etc.}
  \item{Guarding our hearts means to watch our inner man with all vigilance.
  Whatever happens to the heart will affect everything a person does.  I.e,
  if the heart is corrupt, then the affections, motives, pursuits of a person
  will be corrupt. The heart is the core of the person.}
  \item{As Augustine said: ``You have made us for yourself, O Lord, and our
  heart is restless until it rests in you''.  The restlessness is because of
  sin; sin causes us to try to fill our heart with worldly things, which will
  only make us restless, but as we all know only God can fill our heart.}
  \item{The heart is what God transforms in the New Covenant, e.g Jeremiah
  31:33.  And once the heart is transformed, we will have abundant life in
  the sense of John 10:10b.  Also, from John 7:37-38, we see that believing
  in Jesus is the way to have a transformed heart.}
  \item{We guard our hearts practically by Psalm 119:11.  Guarding our hearts
  keeps us from sinning, and helps us to live the abundant life that God has
  for us.  The more we hear God's word, the more we will recognise God's
  voice.}
  \item{In life we watch many worldly things carefully, like our weight, our
  children's grades, sales, etc.  But the text today says, \textbf{above all
  else}, guard your hearts.}
  \item{If we are parents/teachers, we help our kids guard their hearts
  through sound instruction in the fear of God.}
  \item{If we give our hearts to Jesus, Jesus must control everything, not
  just certain portions of our lives.  The heart is the core of the person,
  and if we truly give our heart to Jesus, the entire life will be
  transformed, not just selected portions.}
  \item{Walking in wisdom: first of all, we note that our actions follow our
  beliefs.  Our behavior is a good indication of what is in our heart. Actions here refer to what we say (v24), what we see (v25), and how we walk (v26).
  \begin{itemize}
    \item{By the way, actions here include what we say (v24).  As per what
    Jesus says, what comes from the mouth first comes from the heart.  To
    walk wisely, we must be careful with what we say with our mouths; that is
    a practical application of guarding our hearts.}
    \item{Our actions here also include what we see (v25).  So we should keep
    our eyes on heavenly things, and look at all things in the world through
    the lens of God's word.  Keeping our eyes on heavenly things mean to keep
    heavenly things as our primary motivation, e.g Paul and running the race,
    keeping his eyes on the prize.}
    \item{Our actions here also include what we do with our feet (v26).
    There are two paths we can choose to walk; the straight and the narrow
    path, or the wide path that leads to destruction.  As another application
    of guarding our hearts, we must daily constantly walk on the straight and
    narrow, and turn away from the wide path that leads to destruction.}
  \end{itemize}}
  \item{Our perfect role model for all of the above is our Lord Jesus Christ,
  who perfectly obeyed the voice of His Father and who perfectly did the will
  of His Father.  Because He is the perfect Son, He brings many sons and
  daughters into glory through the cross.  With Christ's help, it is possible
  for us to guard our hearts, through the Holy Spirit that Jesus sends us to
  help us walk in His example.}
  \item{In conclusion, let us guard our hearts and walk in wisdom (which is
  the result/expression of us guarding our hearts), and we can walk in wisdom
  by watching the things we say, the things we see, and the things we choose
  to do (our feet).}

\end{itemize}