\setcounter{figure}{0}

\section{3rd September 2023: Good words}
\subsection*{Text: No specific text for today}
  % \begin{quote}
  %   Bible passage goes here
  % \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{Recap:
  \begin{enumerate}
    \item{Proverbs 18:21. Our words can lead to either good consequences, or bad consequences. We can either uplift someone or hurt someone.}
    \item{Bad words, like lies and hurtful statements, come from a rotten, deceitful heart.}
    \item{We need God’s help to renew our heart so that we can speak gracious words.}
  \end{enumerate}}
  \item{Three points for today:
  \begin{enumerate}
    \item{Why good words matter}
    \item{God's word}
    \item{Relying on the Holy Spirit for God’s help}
  \end{enumerate}}
  \item{Why do good words matter?
  \begin{itemize}
    \item{Proverbs 12:25 — our words can help uplift someone and encourage someone. When someone else is in trouble, we don’t need to lie to the person and tell him that his problem will go away tomorrow, but we can speak truths like how God is with them :).}
    \item{Kind words are like honey, Proverbs 16:24.}
    \item{Our words can often bring healing to people whom we have hurt. An example of that would be an apology. Apologizing is really difficult. Really need God’s help for this. And one thing that is helpful yo remember is that God has forgiven us. See Ephesians 4:32}
  \end{itemize}}
  \item{Why God's word matters
  \begin{itemize}
    \item{Colossians 3:12-17. Love is the key to speaking gracious words. But this Christian love that constantly puts others first doesn’t come from us, it comes from God. God gives us this love through His Word, through Psalms, hymns and spiritual songs (v16). }
    \item{The Spirit of God uses the word of God to put new life in our hearts and new words in our mouths.}
  \end{itemize}}
  \item{Rely on the Spirit for our words
  \begin{itemize}
    \item{1 Corinthians 2:10-13}
    \item{We have received God’s Spirit!}
    \item{And we use words given to us by the Spirit, using the Spirit’s word to explain spiritual truths.}
    \item{We should pray and ask the Spirit for opportunities to share the gospel in our conversations and also for the power to share the gospel in our conversations. }
    \item{We should also ask for and rely on the Spirit’s prompting to find someone that we can encourage with a gracious word.}
    \item{The Spirit works in us to give us a new heart, and the Spirit also works through us and uses us to encourage people, especially other Christians.}
  \end{itemize}}
\end{itemize}