\section{10 April 2022: Blessed is He who comes in the name of the Lord}
\subsection*{Text: Mark 11:1-11}
  \begin{quote}
    [1] Now when they drew near to Jerusalem, to Bethphage and Bethany, at
    the Mount of Olives, Jesus sent two of his disciples [2] and said to
    them, “Go into the village in front of you, and immediately as you enter
    it you will find a colt tied, on which no one has ever sat.  Untie it and
    bring it.  [3] If anyone says to you, ‘Why are you doing this?’ say, ‘The
    Lord has need of it and will send it back here immediately.’” [4] And
    they went away and found a colt tied at a door outside in the street, and
    they untied it.  [5] And some of those standing there said to them, “What
    are you doing, untying the colt?” [6] And they told them what Jesus had
    said, and they let them go.  [7] And they brought the colt to Jesus and
    threw their cloaks on it, and he sat on it.  [8] And many spread their
    cloaks on the road, and others spread leafy branches that they had cut
    from the fields.  [9] And those who went before and those who followed
    were shouting, “Hosanna!  Blessed is he who comes in the name of the
    Lord!  [10] Blessed is the coming kingdom of our father David!  Hosanna
    in the highest!”

    [11] And he entered Jerusalem and went into the temple.  And when he had
    looked around at everything, as it was already late, he went out to
    Bethany with the twelve.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{What Jesus did here was quite different from His previous actions;
  previously He wanted to keep his actions secret, yet in this text He was
  very public.  In the past, Jesus didn't want people to think He was a
  revolutionary who would start a coup, hence His secrecy.  But from this
  portion onwards, Jesus openly confronts the religious leaders in Jerusalem
  for their hypocrisy.  So why would Jesus publicly enter Jerusalem on a
  donkey?  Three points:
  \begin{itemize}
    \item{It is symbolic}
    \item{It is simple(?)}
    \item{It is for suspense}
  \end{itemize}}
  \item{Symbolic: Jesus gives very clear and specific instructions to two of
  His disciples, such as where to find the colt, what to say if they were
  questioned, etc.  In the response `the Lord has need of it', it can either
  mean that the master of the colt needs it, or God needs it.  In verse 2, we
  also see that the colt must not have been sat on before.  This is consonant
  with the OT laws that animals that are used for sacred purposes must not
  have been used before for other stuff.  Here we see that everything Jesus
  does here is intentional.  All his actions are symbols and signs that
  fulfill Old Testament prophecies (e.g Zechariah 9:9).  It shows to the
  people that God remembers and keep His promises about a coming messiah king
  that would come to save His people.  In Zechariah 9:9, we see that the
  coming king will be humble, and this is what exactly Jesus is.  Though
  Jesus is the King of Kings and the Lord of Lords, he entered the city on a
  donkey and on a makeshift saddle.  And looking forward, Jesus will not
  fully display His glory until He goes humbly to the cross.  Also, the
  people's response is from Psalm 118:25-28.  Hosanna used to mean `save us'
  but by that time is also used as a term of worship.  The people's response
  showed that they understood that Jesus was King and savior, though they
  also misunderstoof what Jesus would do as King.}
  \item{Simple: Though His disciples still didn't fully understand what Jesus
  was about to do, they still had faith in Jesus and trusted in Him.  They
  did whatever Jesus told them to do, following His instructions to a T.
  They did not know what the actions would lead to, but their simple faith
  and obedience fulfilled God's purposes.  They recognised that Jesus is the
  messiah king.  Though the disciples are like us, frail and weak, Jesus
  still used them for His purposes.  And from the disciples' POV, through
  their simple faith, they helped to bring about God's plan.}
  \item{Suspense: Will Jesus find His house in order?  From v11, we see that
  the first thing that Jesus did was to enter the temple.  And then
  subsequently, Jesus pronounced judgment on the temple, which similar to OT,
  was an indictment against the religious leaders.}
\end{itemize}
