\section{15th Jan 2023: True Way Vision statement}
\subsection*{Text: Ephesians 3:14-21}
  \begin{quote}
    [14] For this reason I bow my knees before the Father, [15] from whom every family in heaven and on earth is named, [16] that according to the riches of his glory he may grant you to be strengthened with power through his Spirit in your inner being, [17] so that Christ may dwell in your hearts through faith—that you, being rooted and grounded in love, [18] may have strength to comprehend with all the saints what is the breadth and length and height and depth, [19] and to know the love of Christ that surpasses knowledge, that you may be filled with all the fullness of God.

    [20] Now to him who is able to do far more abundantly than all that we ask or think, according to the power at work within us, [21] to him be glory in the church and in Christ Jesus throughout all generations, forever and ever. Amen.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{The understanding of TWPC is this: if we are faithful in our mission,
  we will be able to reach our mark, i.e to achieve our vision.  Church’s new
  vision statement: to be like Jesus, by the power of His Spirit, for the
  glory of God.}
  \item{To be like Jesus means to be like Jesus in His being (His character) and in His actions. For the former, our text says that the church is to be rooted and grounded in love. To be rooted and grounded in love implies that we will be growing in love (a plant is rooted and grounded to grow). Growing in love makes us more like Jesus, since God is love.}
  \item{How to grow in love? Through service!
  \begin{enumerate}
    \item{The one being served experiences God’s love.}
    \item{The one who is serving experiences God’s love.}
    \item{The one who is serving while being stretched grows in love.
    Serving is hard, and we can only serve by depending on the Spirit.  So
    when we serve more, we depend more on the Spirit and we grow in love.}
    \item{Lastly, we can all share how we have experienced God’s love.
    That’s why the text says that when we understand God’s love, we have to
    do so with “all the saints”.  Understanding God’s love is a group
    effort.}
  \end{enumerate}}
  \item{The end goal in this text is this: “to be filled with all the fullness of God”}
  \item{To be like Jesus also means to grow to be like Jesus in his doing. Tangibly, this looks like: When we carry out the mission of pursuing the 4Es (John 20:21, Matthew 28:19).}
  \item{We are not doing all the above alone though, we are doing the above by the power of His Spirit. Jesus Christ is in our midst, as per Matthew 28:20. Jesus is dwells with us through the person of the Spirit in us. Jesus is also with the church, Rev. 2:1. From our text, we see this concept of the Spirit helping us through verses like v16 and v20.}
  \item{Prayer is what helps us to rely on the Spirit working through us.}
  \item{Fell asleep from here onwards...had too little sleep the previous night...}
\end{itemize}