\section{27th February 2022: Fleeing from sexual immorality}
\subsection*{Text: Proverbs 5:1-23}
  \begin{quote}
    [1] My son, be attentive to my wisdom;
        incline your ear to my understanding,
    [2] that you may keep discretion,
        and your lips may guard knowledge.
    [3] For the lips of a forbidden woman drip honey,
        and her speech is smoother than oil,
    [4] but in the end she is bitter as wormwood,
        sharp as a two-edged sword.
    [5] Her feet go down to death;
        her steps follow the path to Sheol;
    [6] she does not ponder the path of life;
        her ways wander, and she does not know it.


    [7] And now, O sons, listen to me,
        and do not depart from the words of my mouth.
    [8] Keep your way far from her,
        and do not go near the door of her house,
    [9] lest you give your honor to others
        and your years to the merciless,
    [10] lest strangers take their fill of your strength,
        and your labors go to the house of a foreigner,
    [11] and at the end of your life you groan,
        when your flesh and body are consumed,
    [12] and you say, “How I hated discipline,
        and my heart despised reproof!
    [13] I did not listen to the voice of my teachers
        or incline my ear to my instructors.
    [14] I am at the brink of utter ruin
        in the assembled congregation.”


    [15] Drink water from your own cistern,
        flowing water from your own well.
    [16] Should your springs be scattered abroad,
        streams of water in the streets?
    [17] Let them be for yourself alone,
        and not for strangers with you.
    [18] Let your fountain be blessed,
        and rejoice in the wife of your youth,
    [19]     a lovely deer, a graceful doe.
    Let her breasts fill you at all times with delight;
        be intoxicated always in her love.
    [20] Why should you be intoxicated, my son, with a forbidden woman
        and embrace the bosom of an adulteress?
    [21] For a man’s ways are before the eyes of the LORD,
        and he ponders all his paths.
    [22] The iniquities of the wicked ensnare him,
        and he is held fast in the cords of his sin.
    [23] He dies for lack of discipline,
        and because of his great folly he is led astray.
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{Sex is a very precicous and powerful gift given to us by God.  It is
  so powerful and precious that if sex is abused, it will have dire
  consequences.  Scripture doesn't pull any punches in this topic, because
  the stakes are high.  This is an issue that affects everyone,
  married/unmarried, men/women. While proverbs 5 is addressed literally to men, we can easily apply it to women. The reason why it is addressed to men is cultural and will not be explored here.}
  \item{Three main points:
  \begin{itemize}
    \item{Attraction: the power of attraction and how it works.}
    \item{Attrition: the wear and tear, the pain and comes our way when we
    fall into sexual immorality.}
    \item{Attention: how are we to discipline our attention to avoid sexual
    immorality.}
  \end{itemize}}
  \item{Attraction: There is hardly a Christian person that wakes up thinking
  ``today I want to fall into sexual immorality''.  But Christians still fall
  nonetheless because we are led along by sin, i.e we are attracted to sin.
  Two avenues by which we are attracted is via the ear and the eye; see
  proverbs 5:3.  And also, by the scent, or by the touch.  Different people
  are more susceptible to different things.  So we must know what our
  weakness is, so we can take appropriate measures to flee.  Specifically for
  the ear and the eye, we have pornography; there are hardly any silent
  pornographic films for example, they use the two-pronged approach.  This is
  an issue that is especially difficult in the Internet age.  There are many
  strategies that we can take to counter this temptation; though those
  strategies can be inconvenient, we \textbf{must} do it, because if we
  don't, we will be led along.}
  \item{Attrition: What if we are led along?  If we are, we can look at
  Proverbs 5:4-14.  I.e, a large proportion of Proverbs 5 describes the great
  and dire consequences of being led along by sexual sin, so that when we
  enter into temptation, we might consider the consequences and get out of
  temptation.  E.g, Proverbs 5:4-5.  There is bitterness, loss of honor, lost
  of years (e.g when your whole life with your spouse come crashing down
  because of infidelity).  Being attracted to sin is like borrowing from a
  loan shark; if we borrow, we might need to pay it back with a lot of
  interest.  E.g for one moment of pleasure with an adulteress, we might need
  to spend many, many years rebuilding family relationships. The price of sexual immorality is real and hefty.
  
  The long description of attrition here also tells us that God wants our
  life to flourish, and that our life flourishes only when we walk according
  to the framework of God's Law, which is the divine design for a flourishing
  human life. We need to daily consider the stakes, to help us flee from sexual immorality.}
  \item{Attention: So what are we to do with this frightening monster?  There
  are external things we can do, but there are also internal things (see
  Proverbs 5:7) we can do, which we shall classify as disciplining our
  attention.  What we give our attention to can be trained; we must be
  intentional about what we think about, what we look at, to know when to
  stay and dwell, to know when to flee like Joseph in Popithar's house.  One
  thing we can dwell in is to our allegiance to our spouse and our family,
  see Proverbs 5:15-20.  We must daily put our attention there, so that when
  temptation comes, we will know that we must flee.  Another idea we can
  dwell in is to discipline our affection; see verse 18.  We must always
  strive to dwell on and develop our affection for our spouse.  If we think
  that our relationship is getting `stale', we must then take time to put our
  attention to appreciate the depths of beauty in our spouse.  People will
  age, but the inner beauty is permanent (charm is deceitful, beauty is vain,
  but the fear of the Lord...).  In fact, the word ``intoxicated'' here for
  the wife is the same as ``leading astray'' used for the adulteress above.
  Thus, the author of Proverbs is contrasting the two types of ``leading
  astray'' here.}
  \item{In conclusion, remember the three points here; the
  \textbf{attraction} of sexual sin, the \textbf{attrition} caused by sexual
  sin, and to discipline our \textbf{attention}.  Especially in the NT
  context, remember that our bodies are temples of the Holy Spirit (1
  Corinthians 6:19-20).  Sexual sin can be forgiven by your spouse, but the
  real life consequences, the hurt and the pain, are real.  Sexual sin can be
  forgiven but not forgotten.  So don't fall into it, consider the
  consequences, and discipline your attention.  And for the unmarried, we
  must still discipline our attention, so that we don't get led astray into
  destruction.  And when we do so, we learn to discern what is important in a
  life partner.}
\end{itemize}