\section{23rd January 2022: A Father's invitation to wisdom}
\subsection*{Text: Proverbs 1}
  \begin{quote}
    [1] The proverbs of Solomon, son of David, king of Israel:

    [2] To know wisdom and instruction,
        to understand words of insight,
    [3] to receive instruction in wise dealing,
        in righteousness, justice, and equity;
    [4] to give prudence to the simple,
        knowledge and discretion to the youth—
    [5] Let the wise hear and increase in learning,
        and the one who understands obtain guidance,
    [6] to understand a proverb and a saying,
        the words of the wise and their riddles.


    [7] The fear of the LORD is the beginning of knowledge;
        fools despise wisdom and instruction.


        [8] Hear, my son, your father’s instruction,
        and forsake not your mother’s teaching,
    [9] for they are a graceful garland for your head
        and pendants for your neck.
    [10] My son, if sinners entice you,
        do not consent.
    [11] If they say, “Come with us, let us lie in wait for blood;
        let us ambush the innocent without reason;
    [12] like Sheol let us swallow them alive,
        and whole, like those who go down to the pit;
    [13] we shall find all precious goods,
        we shall fill our houses with plunder;
    [14] throw in your lot among us;
        we will all have one purse”—
    [15] my son, do not walk in the way with them;
        hold back your foot from their paths,
    [16] for their feet run to evil,
        and they make haste to shed blood.
    [17] For in vain is a net spread
        in the sight of any bird,
    [18] but these men lie in wait for their own blood;
        they set an ambush for their own lives.
    [19] Such are the ways of everyone who is greedy for unjust gain;
        it takes away the life of its possessors.


        [20] Wisdom cries aloud in the street,
        in the markets she raises her voice;
    [21] at the head of the noisy streets she cries out;
        at the entrance of the city gates she speaks:
    [22] “How long, O simple ones, will you love being simple?
    How long will scoffers delight in their scoffing
        and fools hate knowledge?
    [23] If you turn at my reproof,
    behold, I will pour out my spirit to you;
        I will make my words known to you.
    [24] Because I have called and you refused to listen,
        have stretched out my hand and no one has heeded,
    [25] because you have ignored all my counsel
        and would have none of my reproof,
    [26] I also will laugh at your calamity;
        I will mock when terror strikes you,
    [27] when terror strikes you like a storm
        and your calamity comes like a whirlwind,
        when distress and anguish come upon you.
    [28] Then they will call upon me, but I will not answer;
        they will seek me diligently but will not find me.
    [29] Because they hated knowledge
        and did not choose the fear of the LORD,
    [30] would have none of my counsel
        and despised all my reproof,
    [31] therefore they shall eat the fruit of their way,
        and have their fill of their own devices.
    [32] For the simple are killed by their turning away,
        and the complacency of fools destroys them;
    [33] but whoever listens to me will dwell secure
        and will be at ease, without dread of disaster.”
  \end{quote}
\subsection*{Notes}
\begin{itemize}
  \item{Authorship of Proverbs: Mainly Solomon (see chapter 1:1, chapter
  10:1, chapter 25:1) but also others like Agur, Lemuel, ``the wise'', etc.
  Though Solomon's wisdom is greater than all of the others' wisdom (1 Kings
  4:29-34).}
  \item{Apparently, Solomon was also a man of science; his study of nature
  helped him to see wisdom in the created order, like when he provides an
  analogy to the ant to explain the value of hard work and diligence.  As
  will be seen in the later sermons, God's wisdom is baked into the whole
  created order (Proverbs 8, Proverbs 3) and hence one can get wisdom by
  studying the created order.}
  \item{That being said, books of Wisdom like Proverbs, Ecclesiastes, Job are
  revealing divine truths about the world, more than just information about
  the world.}
  \item{Proverbs teaches divine truth, teaching God's people what godly
  living in day to day life looks like.  Though on this note, Proverbs
  teaches us general principles instead of going into specifics; for example,
  in Proverbs 13 when the child and the rod are mentioned, the text does not
  tell us how many times we should use the rod, how much force to use with
  the rod, etc.}
  \item{Again, we must emphasize that that wisdom is from God above (2
  Chronicles 1:8-10), though it is available to all by God's common grace.}
  \item{Proverbs invites us to reflect upon God's truths rather than to
  promise us immediate rewards for our choices.}
  \item{Wisdom literature in its entirety (Job and Ecclesiastes also) teach God's people the entire complexity of life.
  \begin{itemize}
    \item{Proverbs gives us general principles for us to ponder and consider as we think about living righteously.}
    \item{Job and Ecclesiastes handle the edge cases (i.e, exceptions to the
    general principles in Proverbs) that now occur because of sin.  E.g,
    Proverbs say that generally the wicked will suffer for their wickedness,
    but Job and Ecclesiastes show the exceptions to the above general rule.}
  \end{itemize}}
  \item{Wisdom is more about knowledge, it is also about skillfulness (Exodus
  31:1-3).  More than being knowledgeable, being wise is to be skillful in
  applying God's truth in our life.}
  \item{True wisdom is inseparable from righteousness.  Wisdom teaches us how
  to do righteousness, and teaches us how to see beneath the surface to make
  sound judgements.
  \begin{itemize}
    \item{The Law teaches us what is right and wrong, but the emphasis of the
    Law is not on the ``how''.}
    \item{Wisdom emphasises that right living leads to life, wrong living
    leads to death (Proverbs 1:29-32), then goes on to give us general
    principles on what right living looks like.}
  \end{itemize}}
  \item{``Wisdom cries out in the street'' God's wisdom is available to all,
  not hidden.  It is just whether people want to hear or not.}
  \item{Wisdom is received on bended knees (Proverbs 1:7)
  \begin{itemize}
    \item{To fear God is to reverence God and to humbly submit to God's power
    and moral authority over all things.}
    \item{Fools disregard God and ignore God's moral authority, e.g Adam and
    Eve and the Fall.}
    \item{God's moral authority is baked into God's creation, hence people
    who go against God's moral authority go against God's created order and
    hence generally hurt themselves.  E.g, addiction to drugs, addiction to
    pornography, sex outside of marriage etc all are scientifically proven to
    cause harm to a person.
    \begin{itemize}
      \item{Though we must emphasize again that the devastating effect of
      going against God's wisdom in the created order is obscured because of
      sin, i.e sin throws the balance of the creation abit off (e.g thorns
      and thistles), and sin darkens our mind such that we don't really see
      the devastating, natural consequences of sin until it is too late.}
    \end{itemize}}
  \item{Wisdom from God is best exemplified in Jesus (1 Corinthians 1:30).
  Fear of God will lead us to be transformed through jesus.  Not our own
  wisdom that transforms us, but Jesus makes us wise.}
  \item{Wisdom is learnt not alone, but in the context of community and
  discipleship}
  \end{itemize}}
\end{itemize}